---
title: "DS_P8105_hw1_qx2222"
author: "Qiaoyi Xu"
date: "2022-09-18"
output: github_document
---

```{r,results='hide'}
library(tidyverse)
```


**Problem 1**

###load the penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
print(penguins) 
```

###description of the penguins dataset


1. In "penguins" dataset, names of important variables are `r colnames(penguins)`. Among those important varibales, there are three types of value, <fctr>(factor,  categorical variables with fixed possible values), <dbl>(numeric values with decimal points), <int>(integer values).

2. The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` column.

3. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.


###create scatter plot

```{r, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("penguins_scatter_prob1.pdf", width = 4, height = 6)
```

**Problem 2**

###create the dataframe

```{r}
df_prob2 = tibble(
  norm_sample = rnorm(n=10),
  vec_logical = norm_sample>0,
  vec_char = c("a", "b","c", "d", "e","f","j","h", "i", "g"),
  vec_factor = factor(c("low", "medium", "high", "low", "medium", "high","low", "medium", "high", "low"))
)

df_prob2

```

###calculate the mean of each variable in dataframe

```{r, warning=FALSE}
mean(pull(df_prob2, var = norm_sample)) #mean of norm_sample variable
mean(pull(df_prob2, var = vec_logical)) #mean of vec_logical variable
mean(pull(df_prob2, var = vec_char)) #mean of vec_char variable
mean(pull(df_prob2, var = vec_factor)) #mean of vec_factor variable
```
From the output, the means of norm_sample variable and vec_logical variable could be calculated. However, it doesn't work to calculate the means of vec_char variable and vec_factor variable. 
